---
title: "Untitled"
author: "Eddie Liu"
date: "December 12, 2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


# Introduction and Research Objective

AirBNB's website has a collection of datasets that summarize its user's listings internationally. Our group picked the listings dataset of the greater Los Angeles area and is interested in analyzing possible factors that affect the rental prices. Because there is information for over 200 neighorhoods, we looked at the rentals of the major cities in western Los Angeles. Specifically, we want to know if the room type and location, described as neighborhood in the dataset, affect the price of the rental. Using a multiple linear regression model, we attempt to quantify the significance of the variables of interest. 


# Graphics

```{r, fig.align='center', fig.cap='Price for each room type and neighborhood', fig.height=6, fig.width = 12, warning=F, message=F}
listings <- read.csv("airbnb.csv", header = T)
vec <- c('Culver City', 'Beverly Hills', 'Santa Monica', 'Malibu', 'West Hollywood', 'Westwood', 'Westchester', 'Venice', 'Sawtelle', 'Century City')
dat <- listings[which(listings$neighbourhood %in% vec), ] 
dat <- dat[, -c(1, 2, 3, 4, 5, 7, 8, 11, 12, 13, 14, 15, 16)]
require(ggplot2)
h <- ggplot(data = dat, mapping = aes(y = log(price), x = room_type, color = neighbourhood)) + geom_point()
plot(h)
```


```{r, warning=F, message=F, fig.height = 8, fig.width = 12, fig.cap ='Average price in each neighborhood', fig.align='center'}
library(reshape2)
library(dplyr)
ggplot(data = reshape2::melt(dat), aes(x = neighbourhood, y = log(value), color = neighbourhood)) + 
  geom_point() +
  stat_summary(
    geom = "point",
    fun.y = "mean",
    col = "black",
    size = 3,
    shape = 24,
    fill = "red")
```

```{r, fig.align='center', fig.cap='Relationship between number of nights, price, and room type', fig.height=6, fig.width = 12, warning=F, message=F}
#Preliminary plot
ggplot(listings, aes(x = minimum_nights, y = price, color = room_type)) + geom_point() + xlab("Minimum # of Nights") + ylab("Price") + ggtitle("Relationship Between Minimum # of Nights and Price") + labs(colour = "Room Type") + theme(plot.title = element_text(hjust = 0.5))
```

```{r, fig.align='center', fig.cap='Correlation Test between minimum nights and price', fig.height=6, fig.width = 12, warning=F, message=F}
library(ggpubr)
airbnb <- listings
ggscatter(airbnb, x = "minimum_nights", y = "price", add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson", xlab = "Minimum # of Nights", ylab = "Price")

```


# R Code for Analysis

```{r}
dat2 <- dat[, -2]
dat2 <- dat2[-c(3174, 3595, 3606, 3744), ]
dat2$price <- log(dat2$price)
```


```{r}
dat2 %>% group_by(neighbourhood) %>% summarise_all(mean)
dat <- dat[-c(3174, 3595, 3606, 3744), ]
anova(lm(price~neighbourhood+room_type, data = dat))
print(summary(lm(log(price)~neighbourhood+room_type, data = dat)))
```


# Results

From the ANOVA table, the p-value of 0 suggests that the overall model is significant; that is, the type of neighborhood and room type are significant in predicting the price. Furthermore, the summary of the log-linear model specifies that each city is significant in predicting the price. The type of room was only signifiant if it was a private or shared room. Although our R-squared value of 0.4146 is relatively small, it is clear that the two predictors do a good job of explaining part of the variation in price. 


# Summary

Our group is interested in AirBNB's Los Angeles dataset and wants to determine if certain variables can predict the price of a given rental. Specifically, we examined the variables neighborhood and type of room. We created graphics to visualize the difference of price per room type and price difference per neighborhood. There seemed to be a difference in price based on each of these variables, so we analyzed the data numerically and found that both were significant. From our third graphic, we concluded that there did not seem to be a relationship between the price and the minimum number of nights required for a listing, but we did see that room type and price were correlated with entire homes/ apartments costing more on average. 
